Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/evaluation.tex
Several changes.
Cganhges.

\paragraph{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse, and was acquired using ssEM. The dataset resolution is $3\times3\, \text{nm}^2$ per pixel, with section thickness of $30\, \text{nm}$. Image data and a manually-labeled expert `ground truth' segmentation is available publicly for the entire dataset\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.

@@

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

\paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means a better match to ground truth. We treat VI as a continuous variable during analysis.

>>>>

\paragraph{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse, and was acquired using ssEM. The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$. Image data and a manually-labeled expert `ground truth' segmentation is available publicly for the entire dataset\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.

@@

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

\paragraph{Evaluation metric.} We measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).% We treat VI as a continuous variable during analysis.
